Proportional Occupancy

### 2021-07-12 R/PropOcDataThor.Rmd

GetPropOcData<-function(sampleName, xyDim,zDim){
  tic()
  parentFolder<- '/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
  #parentFolder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
  sampleFolder<-paste0(parentFolder, sampleName)
  attrList<-str_split(sampleName,"_")[[1]]
  print(sampleName)
  fileList<-list.files(path = sampleFolder, full.names = TRUE)
  print(paste("# of files:", length(fileList)))
  if(length(fileList)<1){
    print("empty set")
  }else{
  greenImg<-fileList[grep("G_",fileList)]
  redImg<-fileList[grep("R_",fileList)]
  propOcData<-AllDataPipeline(Slices2threeD(redImg),Slices2threeD(greenImg), 
                                     xydimSearch=round(30/xyDim),zdimSearch =round(30/zDim),
                                     sampleSize=10,xyRealDim=xyDim,
                                     zRealDim = zDim, pipeBinSize = 1)
  propOcData$Condition <- attrList[1]
  propOcData$TimePoint <- attrList[2]
  propOcData$Replicate <- attrList[3]
  write.csv(propOcData, paste0("/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data/",sampleName,".csv"))
  toc()}
  }

testGetPropOcData<-GetPropOcData("wt_d1_02", .415,.52)
testGetPropOcDataemptyFolder<-GetPropOcData("wt_d1_01", .415,.52)

@@

testSlices2threeD<-Slices2threeD(testGrepG)
testGrepG[1]
testImage1<-as.array(readImage(testGrepG[1], convert = TRUE))
install.packages("BiocManager")
BiocManager::install("EBImage")
```

>>>>

for(row in 1:length(metaData.df[[1]])){
  metaData.df$Condition[[row]] = str_split(metaData.df$SampleCode[[row]],"_")[[1]][[1]]
}
metaData.df<-metaData.df %>% filter(!is.na(mouse))#removes the last row

metaData.df<- metaData.df %>% #remove samples that have already ran
  filter(!SampleCode == "pqsL_d4_16") %>%
  filter(!SampleCode == "mono_d1_03") %>%#stalled
  filter(!SampleCode == "mono_d1_02") %>% #ran
  filter(!SampleCode == "mono_d1_01") %>% #ran
  filter(!SampleCode == "mono_d1_04") %>% #ran
  filter(!SampleCode == "mono_d1_05") %>% #ran
  filter(!SampleCode == "mono_d1_06") %>%  #seemed to have stalled but data file is saved
  filter(!SampleCode == "mono_d1_07") %>% #seemed to have stalled but data file is saved
  filter(!SampleCode == "mono_d1_08") %>%
  filter(!SampleCode == "mono_d1_09") %>%
  filter(!SampleCode == "mono_d1_10") %>%
  filter(!SampleCode == "mono_d1_11") %>%
  filter(!SampleCode == "mono_d1_12") %>%
  filter(!SampleCode == "mono_d1_13") %>%
  filter(!SampleCode == "mono_d1_14") %>%
  filter(!SampleCode == "mono_d1_15") %>%
  filter(!SampleCode == "mono_d4_01") %>%
  filter(!SampleCode == "mono_d4_02") %>%
  filter(!SampleCode == "mono_d4_03") %>%
  filter(!SampleCode == "mono_d4_04")

metaData.df<-metaData.df %>% filter(!Condition == "mono") %>% 
  filter(!Condition == "pawt") %>% 
  filter(!Condition == "paphz") %>% 
  filter(!Condition == "papqsL")

  tic()
  parentFolder<- '/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
  #parentFolder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
  sampleFolder<-paste0(parentFolder, sampleName)
  attrList<-str_split(sampleName,"_")[[1]]
  print(sampleName)
  fileList<-list.files(path = sampleFolder, full.names = TRUE)
  print(paste("# of files:", length(fileList)))
  if(length(fileList)<1){
    print("empty set")
  }else{
  greenImg<-fileList[grep("G_",fileList)]
  redImg<-fileList[grep("R_",fileList)]
  propOcData<-AllDataPipeline(Slices2threeD(redImg),Slices2threeD(greenImg), 
                                     xydimSearch=round(30/xyDim),zdimSearch =round(30/zDim),
                                     sampleSize=1000,xyRealDim=xyDim,
                                     zRealDim = zDim, pipeBinSize = 1)
  propOcData$Condition <- attrList[1]
  propOcData$TimePoint <- attrList[2]
  propOcData$Replicate <- attrList[3]
  write.csv(propOcData, paste0("/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data/",sampleName,".csv"))
  toc()}
  }

testGetPropOcData<-GetPropOcData("phz_d4_08", .415,.52)
testGetPropOcDataemptyFolder<-GetPropOcData("wt_d1_01", .415,.52)

@@
